Git and Github Example and Tutorial, Sync with Multiple Repositories, Store Password

### 2020-01-03 nontex/install/git/fs_git_setup.tex
set up compile minor update

@@

\title{New Computer Fan Data-Science Set-up\\
Python (Anaconda), R (Rstudio), Matlab and Latex (Texlive)\\
Atom, VScode, Pycharm}
\author{}
\date{\vspace{-2.5em}}

@@

\hypertarget{objective}{%
\section{Objective}\label{objective}}

Install various compilers and IDE:

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  Python (Anaconda, Pycharm + VSCode + Atom)
\item
  R (VSCode + Atom)
\item
  Matlab
\item
  Latex and PDF (texlive, Okular, VSCode + Atom + Texstudio)
\end{enumerate}

Test at the end:

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  Do sample \emph{py} files work?

  \begin{itemize}
  \tightlist
  \item
    work from command line
  \item
    work from atom (hydrogen), Pycharm, VSCode
  \end{itemize}
\item
  Do sample \emph{rmd} files work?

  \begin{itemize}
  \tightlist
  \item
    work from r-studio
  \item
    work from atom (hydrogen), VSCode
  \end{itemize}
\item
  Do tex templates compile?

  \begin{itemize}
  \tightlist
  \item
    tikz files, template files with bib
  \item
    work from texstudio, VSCode live compile, Atom
  \end{itemize}
\end{enumerate}

Installation Plan outline:

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  Conda install (python)
\item
  Install Atom along with Hydrogen and other packages.
\end{enumerate}

\hypertarget{python-and-anaconda-installation}{%
\section{Python and Anaconda
Installation}\label{python-and-anaconda-installation}}

Use conda across platforms, so that locally on windows and ubuntu and
remotely on aws, can have the same software setup environment.

\begin{itemize}
\tightlist
\item
  Search for Anaconda Prompt, right click, choose run as administrator.
\item
  Check software versions.
\end{itemize}

\begin{Shaded}
\begin{Highlighting}[]
\ExtensionTok{conda}\NormalTok{ list anaconda}
\ExtensionTok{python}\NormalTok{ -V}
\end{Highlighting}
\end{Shaded}

\hypertarget{first-time-conda-install}{%
\subsection{First Time Conda Install}\label{first-time-conda-install}}

\href{https://www.anaconda.com/distribution/}{Download Anaconda Python
3} and install for all users. Afterwards, Anaconda does not
automatically get added to Windows Path. Need to use Anaconda Prompt to
access programs. To access Anaconda packages from windows prompt, from
git bash, from R, etc, need to Add Anaconda to Windows Path.

To install conda in Linux/Debian, follow
\href{https://fanwangecon.github.io/Tex4Econ/nontex/install/linux/fn_ubuntu.html}{these
instructions}. Overall, installations are very similar.

In command/anaconda prompt:

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{# To remove conda Fully}
\FunctionTok{rm}\NormalTok{ -rf ~/anaconda3}

\ExtensionTok{where}\NormalTok{ anaconda}
\CommentTok{# C:/ProgramData/Anaconda3/Scripts/anaconda.exe}
\ExtensionTok{where}\NormalTok{ python}
\CommentTok{# C:/ProgramData/Anaconda3/python.exe}
\ExtensionTok{where}\NormalTok{ jupyter}
\CommentTok{# C:/ProgramData/Anaconda3/Scripts/jupyter.exe}
\ExtensionTok{where}\NormalTok{ jupyter-kernelspec}
\CommentTok{# if R installed already}
\ExtensionTok{where}\NormalTok{ r}

\CommentTok{###############################}
\CommentTok{# Add these to Windows PATH:}
\CommentTok{###############################}
\CommentTok{# C:\textbackslash{}ProgramData\textbackslash{}Anaconda3\textbackslash{}Scripts}
\CommentTok{# C:\textbackslash{}ProgramData\textbackslash{}Anaconda3}
\end{Highlighting}
\end{Shaded}

To Add Anaconda to Path, In Windows 1. Search for: Environment Variables
2. Edit Environment Variables 3. Add new to Path (lower half): -
C:/ProgramData/Anaconda3/Scripts/ - C:/ProgramData/Anaconda3/ 4. Now
open up regular windows command Prompt, Type in: - conda --version -
also Close and Open up Git Bash: conda --version

\hypertarget{conda-update}{%
\subsection{Conda Update}\label{conda-update}}

Open up Anaconda Navigator, it will update navigator automatically. If
there are errors, might have to clean first.

There are different channels/repositories from which packages could be
installed: \emph{conda}, \emph{conda-forge}, for example. Can change
where to look for packages first. Many packages are in multiple
channels. Conda-forge often have mroe recent packages.

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{# if there are bugs}
\CommentTok{# conda clean --packages}
\CommentTok{# use conda-forge as main channel, more updated packages}
\ExtensionTok{conda}\NormalTok{ config --get channels}
\ExtensionTok{conda}\NormalTok{ config --add channels conda-forge}
\ExtensionTok{conda}\NormalTok{ config --get channels}
\CommentTok{# remove conda-forge from channels (do so for main env install)}
\ExtensionTok{conda}\NormalTok{ config --remove channels conda-forge}
\CommentTok{# normal update}
\ExtensionTok{conda}\NormalTok{ update --all}

\CommentTok{# install additional packages}
\ExtensionTok{conda}\NormalTok{ install -y statsmodels datashape seaborn}
\ExtensionTok{conda}\NormalTok{ install -c conda-forge -y interpolation awscli}
\ExtensionTok{conda}\NormalTok{ install -c anaconda -y boto3}
\end{Highlighting}
\end{Shaded}

\hypertarget{python-command-line-test}{%
\subsection{Python Command Line Test}\label{python-command-line-test}}

Fist test python under command line:

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{# windows}
\ExtensionTok{python} \StringTok{"C:/Users/fan/PyFan/ProjectSupport/Testing/Numpy/Functions.py"}
\ExtensionTok{python} \StringTok{"C:/Users/fan/PyFan/ProjectSupport/graph/subplot.py"}
\CommentTok{# linux}
\ExtensionTok{python}\NormalTok{ ~/PyFan/ProjectSupport/Testing/Numpy/Functions.py}
\ExtensionTok{python}\NormalTok{ ~/PyFan/ProjectSupport/graph/subplot.py}
\end{Highlighting}
\end{Shaded}

\hypertarget{r-installation}{%
\section{R Installation}\label{r-installation}}

R could be installed from Anaconda or directly on windows outside of the
Anaconda directories. When installing from within Anaconda, could create
R environment that are isolated from the rest of the computer. The R
environment could be updated and deleted without disturbing dependencies
in conda main or the rest of the computer.

The computer could have multiple R installations. Several in different
conda R environment, and also several under windows/linux primary main
user R directories. Type \emph{which R/where R} to see if you open up R
from command line at the moment, which directory's R will be used.
Inside Conda R environment, it will be a different R if there is a
different R version there.

\hypertarget{fully-uninstall-r}{%
\subsection{Fully Uninstall r}\label{fully-uninstall-r}}

If R was installed in R enviornments, just delete the environment.
Otherwise, use system's uninstaller. Before that, from
terminal/command-prompt, type \emph{R}, and \emph{.libPaths()} to find
paths. Do so inside conda main, outside of conda main, inside different
environments, find all paths. After uninstaller finishes, check in the
libPath folders to see if there are still stuff there, delete all,
delete the folders.

\begin{Shaded}
\begin{Highlighting}[]
\KeywordTok{.libPath}\NormalTok{()}
\CommentTok{# C:/Users/fan/Documents/R/win-library/3.6}
\CommentTok{# C:/Program Files/R/R-3.6.1/library}
\end{Highlighting}
\end{Shaded}

For Linux and for unsintalling inside conda:

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{# Exit Conda}
\ExtensionTok{conda}\NormalTok{ deactivate}
\CommentTok{# where is R installed outside of Conda}
\FunctionTok{which}\NormalTok{ R}
\CommentTok{# /usr/bin/R}
\CommentTok{# To remove all}
\FunctionTok{sudo}\NormalTok{ apt-get remove r-base}
\FunctionTok{sudo}\NormalTok{ apt-get remove r-base-core}

\CommentTok{# Inside Conda base}
\ExtensionTok{conda}\NormalTok{ activate}
\CommentTok{# Conda r_env}
\ExtensionTok{conda}\NormalTok{ activate r_env}
\CommentTok{# Where is it installed?}
\FunctionTok{which}\NormalTok{ R}
\CommentTok{# /home/wangfanbsg75/anaconda3/bin/R}
\ExtensionTok{conda}\NormalTok{ uninstall r-base}
\end{Highlighting}
\end{Shaded}

\hypertarget{install-r-outside-of-conda}{%
\subsection{Install R (outside of
Conda)}\label{install-r-outside-of-conda}}

Need to install R. Then need to install also an editor/IDE for R.
Rstudio is the dominant R IDE. VSCode and Atom also works well,
especially VSCode as editors. Dramatically better experience for writing
scripts outside of Rstudio which feels unwieldy and slow especially
compared to VSCode.

Overall plan:

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  \href{https://cloud.r-project.org/}{download R}

  \begin{itemize}
  \tightlist
  \item
    for debian:
    \href{https://cran.r-project.org/bin/linux/debian/}{Johannes Ranke}.
    For Linux/Debian installation, crucial to update the
    \emph{source.list} to include sources that have more recent versions
    of R. If not, will get very old R versions that is not compatible
    with many packages.
  \item
    add R to path for Windows. In Windows Path, add for example:
    \emph{C:/Program Files/R/R-3.6.2/bin/x64/} and \emph{C:/Rtools/bin}
  \end{itemize}
\item
  \href{https://rstudio.com/products/rstudio/download/}{download
  R-studio}
\item
  Open R-studio and auto-detect R
\item
  Install additional packages (from commandline)

  \begin{itemize}
  \tightlist
  \item
    various R data-science packages have dependencies, and additional
    not-R programs might need to be installed. Install them as needed,
    for example: \emph{libcurl4-openssl-dev} and \emph{libssl-dev} from
    command prompt first inside Debian.
  \end{itemize}
\end{enumerate}

\hypertarget{linux-r-install}{%
\subsubsection{Linux R Install}\label{linux-r-install}}

For linux/Debian, to Install latest R:

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{# Go to get latesdebian latest r sources.list}
\FunctionTok{cat}\NormalTok{ /etc/apt/sources.list}
\CommentTok{# Install this First (should already be installed)}
\FunctionTok{sudo}\NormalTok{ apt install dirmngr}

\CommentTok{# Debian R is maintained by Johannes Ranke, copied from https://cran.r-project.org/bin/linux/debian/:}
\ExtensionTok{apt-key}\NormalTok{ adv --keyserver keys.gnupg.net --recv-key }\StringTok{'E19F5F87128899B192B1A2C2AD5F960A256A04AF'}
\CommentTok{# Add to source.list, for debian stretch (9)}
\CommentTok{# sudo su added for security issue as super-user}
\FunctionTok{sudo}\NormalTok{ su -c }\StringTok{"sudo echo 'deb http://cloud.r-project.org/bin/linux/debian stretch-cran35/' >> /etc/apt/sources.list"}
\CommentTok{# if added wrong lines, delete 3rd line}
\FunctionTok{sudo}\NormalTok{ sed }\StringTok{'3d'}\NormalTok{ /etc/apt/sources.list}

\CommentTok{# Update and Install R, should say updated from cloud.r}
\FunctionTok{sudo}\NormalTok{ apt-get update}
\FunctionTok{sudo}\NormalTok{ apt-get install r-base r-base-dev}

\CommentTok{# Also install these, otherwise r-packages do not install}
\CommentTok{# libxml2 seems need for tidymodels}
\FunctionTok{sudo}\NormalTok{ apt-get install libcurl4-openssl-dev}
\FunctionTok{sudo}\NormalTok{ apt-get install libssl-dev}
\FunctionTok{sudo}\NormalTok{ apt-get install libxml2-dev}
\end{Highlighting}
\end{Shaded}

\hypertarget{install-packages-for-r}{%
\subsubsection{Install Packages for R}\label{install-packages-for-r}}

From command prompt, enter R by typeing \emph{R}, and install packages:

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{# Can enter R from Command Prompt Conda ENV, much faster than from r-studio}
\CommentTok{# Install R-tools, RTOOLS is for WINDOWS}
\KeywordTok{install.packages}\NormalTok{(}\StringTok{"installr"}\NormalTok{)}
\KeywordTok{library}\NormalTok{(}\StringTok{"installr"}\NormalTok{)}
\KeywordTok{install.Rtools}\NormalTok{()}
\CommentTok{# c:/Rtools/bin;}
\CommentTok{# c:/Rtools/mingw_32/bin;}
\CommentTok{# c:/Rtools/mingw_64/bin;}

\CommentTok{# main packagevps}
\CommentTok{# tidymodel installation on linux difficult}
\KeywordTok{install.packages}\NormalTok{(}\KeywordTok{c}\NormalTok{(}\StringTok{"tidyverse"}\NormalTok{, }\StringTok{"tidymodels"}\NormalTok{, }\StringTok{"tidyr"}\NormalTok{))}
\CommentTok{# development packages}
\KeywordTok{install.packages}\NormalTok{(}\KeywordTok{c}\NormalTok{(}\StringTok{"devtools"}\NormalTok{, }\StringTok{"IRkernel"}\NormalTok{, }\StringTok{"pkgdown"}\NormalTok{, }\StringTok{"roxygen2"}\NormalTok{, }\StringTok{"kableExtra"}\NormalTok{))}
\CommentTok{# other packages}
\KeywordTok{install.packages}\NormalTok{(}\KeywordTok{c}\NormalTok{(}\StringTok{"AER"}\NormalTok{, }\StringTok{"minpack.lm"}\NormalTok{, }\StringTok{"knitr"}\NormalTok{, }\StringTok{"matlab"}\NormalTok{))}

\CommentTok{# Install my package, need to prepare package to work for ubuntu}
\CommentTok{# if install does not work, load locally}
\NormalTok{devtools}\OperatorTok{::}\KeywordTok{install_github}\NormalTok{(}\StringTok{"fanwangecon/R4Econ"}\NormalTok{)}

\CommentTok{# Kernel}
\KeywordTok{install.packages}\NormalTok{(}\KeywordTok{c}\NormalTok{(}\StringTok{'repr'}\NormalTok{, }\StringTok{'IRdisplay'}\NormalTok{, }\StringTok{'evaluate'}\NormalTok{, }\StringTok{'crayon'}\NormalTok{, }\StringTok{'pbdZMQ'}\NormalTok{, }\StringTok{'devtools'}\NormalTok{, }\StringTok{'uuid'}\NormalTok{, }\StringTok{'digest'}\NormalTok{))}
\NormalTok{IRkernel}\OperatorTok{::}\KeywordTok{installspec}\NormalTok{()}
\end{Highlighting}
\end{Shaded}

\hypertarget{install-r-inside-conda}{%
\subsection{Install R (inside Conda)}\label{install-r-inside-conda}}

Key packages are generally available in conda's default channel
(official distribution) and also the more frequently updated conda-forge
channel. Prioritize conda-forge to get the latest packages. After adding
\emph{conda-forge} to channels, that will be prioritized, so when
creating a new environment, conda will install first from conda-forge if
package exists there. Try the \emph{r\_env} generation line with and
without first adding \emph{conda-forge} to channel, and see that the
packages installed will have different versions, reflecting versions in
the default channel and in the \emph{conda-forge} channels.

\hypertarget{set-up-conda-r-environment}{%
\subsubsection{Set up Conda R
environment}\label{set-up-conda-r-environment}}

Create a Conda Environment called \emph{r\_env}, and update its
channels.

\begin{itemize}
\tightlist
\item
  \textbf{Location}: Installed environments are shown appear in the
  \emph{envs} folder of \emph{C:/ProgramData/Anaconda3/envs/}. Can be
  easily deleted without disrupting the main base installation for
  conda. This is very important. During installation, could easily run
  into problems, and need to re-install. Much better to only re-install
  a folder. Note that when R is installed in \emph{envs}, it will not
  show up under add or remove programs for uninstallation from there,
  has to be uninstalled, deleted directly here.
\item
  \textbf{Use only in Env}: Note that if we installed r inside r\_env,
  if we type \emph{r} under the base environment, we can not enter r. We
  can only enter r within r\_env. With PATH properly set-up, this
  happens under Conda Prompt, Windows Prompt, etc.
\item
  \textbf{Multiple Pythons}: With the above installation for R, one
  benefit is that if R requires a different version of Python than what
  the base environment uses, the r\_env could have a different python
  version. So type \emph{python} in the base environment as well as
  inside the \emph{r\_env}. This also means potentially there could be
  duplicated installations I think. Look at the python versions under
  \emph{conda list} in the base and in the r-environment.
\item
  \textbf{File Size}: Note that this creates a large installation
  folder, \emph{C:/ProgramData/Anaconda3/envs/r\_env/}, without
  additional packages, is 1.3 GB in size
\end{itemize}

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{# outside of conda, install some depencies}
\FunctionTok{sudo}\NormalTok{ apt-get install libcurl4-openssl-dev}
\FunctionTok{sudo}\NormalTok{ apt-get install libssl-dev}
\FunctionTok{sudo}\NormalTok{ apt-get install libxml2-dev}

\CommentTok{# install key r packages within a r-environment}
\ExtensionTok{conda}\NormalTok{ env remove -n r_env}
\CommentTok{# start empty environment}
\ExtensionTok{conda}\NormalTok{ create -n r_env}
\CommentTok{# activate env and check, nothing yet}
\ExtensionTok{conda}\NormalTok{ activate r_env}
\ExtensionTok{conda}\NormalTok{ list}

\CommentTok{# check channel and add env specific channel}
\ExtensionTok{conda}\NormalTok{ config --get channels}
\CommentTok{# to get latest r, use conda-forge, which has more recent Rs}
\CommentTok{# conda config --env --add channels conda-forge}
\CommentTok{# channels for base}
\ExtensionTok{conda}\NormalTok{ config --get channels}
\CommentTok{# channels for cur env}
\ExtensionTok{conda}\NormalTok{ config --get channels --env}

\CommentTok{# see all installed environments}
\ExtensionTok{conda}\NormalTok{ env list}
\CommentTok{# activate an environment to use it, if in base, r does not exist, isolated in r_env}
\ExtensionTok{conda}\NormalTok{ activate r_env}
\CommentTok{# see packages in environment}
\ExtensionTok{conda}\NormalTok{ list}
\CommentTok{# to quit}
\ExtensionTok{conda}\NormalTok{ deactivate}
\end{Highlighting}
\end{Shaded}

\hypertarget{install-r-and-some-packages-in-conda}{%
\subsubsection{Install R and Some Packages in
Conda}\label{install-r-and-some-packages-in-conda}}

Either inside a R specific environment, or outside of it, now do
additional installations for R and also R packages.

During installation, the R programs might require downgrading other
programs in the Conda environment that Python for example also uses.
That is why potentially it is safer to install in R environment.
However, when installing in R enviornment, certain packages could have
issues if installer does not realize it is in an environment with
special folder structure, so installation could fail.

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{# install files}
\ExtensionTok{conda}\NormalTok{ install -n r_env -c r r r-essentials r-tidyverse r-tidymodels -y}

\CommentTok{# trouble with igraph installation, install here from conda}
\CommentTok{# conda install -n r_env r-essentials r-base r-tidyr r-tidyverse r-devtools r-irkernel r-pkgdown r-roxygen2}
\ExtensionTok{conda}\NormalTok{ install -n r_env -c r r-igraph}
\ExtensionTok{conda}\NormalTok{ install -n r_env -c conda-forge igraph}
\ExtensionTok{conda}\NormalTok{ install -n r_env -c r r-rstantools r-rstan r-rstanarm -y}
\end{Highlighting}
\end{Shaded}

\hypertarget{install-additional-packages-inside-the-r}{%
\subsection{Install Additional Packages inside the
R}\label{install-additional-packages-inside-the-r}}

These are packages that I use, these should be installed inside the
environment. Or they could be installed later from inside r-studio.
Installing inside r-studio is a lot better. \emph{tidymodel} has
installation issues sometimes.

In \emph{r\_env}, type in \emph{R}, and then install from inside
terminal's R. For conda env, devtools will be installed and will install
packages inside \emph{envs/r\_env/Lib/R}.

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{# enter into env}
\CommentTok{# conda activate r_env}
\CommentTok{# enter R or type in rstudio}
\CommentTok{# sicne R is only install inside r_env, has to enter rstudio from r_env}
\CommentTok{# R}
\CommentTok{# rstudio}

\CommentTok{# main packagevps}
\CommentTok{# tidymodel installation on linux difficult}
\KeywordTok{install.packages}\NormalTok{(}\KeywordTok{c}\NormalTok{(}\StringTok{"rstantools"}\NormalTok{, }\StringTok{"rstan"}\NormalTok{, }\StringTok{"rstanarm"}\NormalTok{))}
\KeywordTok{install.packages}\NormalTok{(}\KeywordTok{c}\NormalTok{(}\StringTok{"tidyr"}\NormalTok{, }\StringTok{"tidyverse"}\NormalTok{, }\StringTok{"tidymodels"}\NormalTok{))}

\CommentTok{# tidymodels}
\CommentTok{# development packages}
\KeywordTok{install.packages}\NormalTok{(}\KeywordTok{c}\NormalTok{(}\StringTok{"devtools"}\NormalTok{, }\StringTok{"IRkernel"}\NormalTok{, }\StringTok{"pkgdown"}\NormalTok{, }\StringTok{"roxygen2"}\NormalTok{, }\StringTok{"kableExtra"}\NormalTok{))}
\CommentTok{# other packages}
\KeywordTok{install.packages}\NormalTok{(}\KeywordTok{c}\NormalTok{(}\StringTok{"AER"}\NormalTok{, }\StringTok{"minpack.lm"}\NormalTok{, }\StringTok{"knitr"}\NormalTok{, }\StringTok{"matlab"}\NormalTok{))}

\CommentTok{# Install my package, need to prepare package to work for ubuntu}
\CommentTok{# if install does not work, load locally}
\NormalTok{devtools}\OperatorTok{::}\KeywordTok{install_github}\NormalTok{(}\StringTok{"fanwangecon/R4Econ"}\NormalTok{)}

\CommentTok{# Kernel}
\KeywordTok{install.packages}\NormalTok{(}\KeywordTok{c}\NormalTok{(}\StringTok{'repr'}\NormalTok{, }\StringTok{'IRdisplay'}\NormalTok{, }\StringTok{'evaluate'}\NormalTok{, }\StringTok{'crayon'}\NormalTok{, }\StringTok{'pbdZMQ'}\NormalTok{, }\StringTok{'devtools'}\NormalTok{, }\StringTok{'uuid'}\NormalTok{, }\StringTok{'digest'}\NormalTok{))}
\NormalTok{IRkernel}\OperatorTok{::}\KeywordTok{installspec}\NormalTok{()}
\end{Highlighting}
\end{Shaded}

\hypertarget{r-studio-set-up-download-from-rstudio}{%
\subsection{R-Studio Set-up Download from
Rstudio}\label{r-studio-set-up-download-from-rstudio}}

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  Download R-studio, and install, as normal (not from conda, directly
  from rstudio website latest windows version)
\item
  Open up anaconda prompt, enter \emph{r\_env} environment:
  \emph{activate r\_env}
\item
  cd into rstudio exe file folder: cd ``C:/Program Files/RStudio/bin''
\item
  start r-studio from inside \emph{r\_env}: rstudio.exe
\item
  inside r-studio, check: \emph{.libPaths()}

  \begin{itemize}
  \tightlist
  \item
    ``C:/ProgramData/Anaconda3/envs/r\_env/Lib/R/library''
  \end{itemize}
\end{enumerate}

\begin{Shaded}
\begin{Highlighting}[]
\ExtensionTok{activate}\NormalTok{ r_env}
\BuiltInTok{cd} \StringTok{"C:/Program Files/RStudio/bin"}
\ExtensionTok{rstudio.exe}

\BuiltInTok{cd} \StringTok{"C:/ProgramData/Anaconda3/envs/r_env/Lib/R/library"}
\StringTok{"C:/Program Files/RStudio/bin/rstudio.exe"}
\end{Highlighting}
\end{Shaded}

For linux, note that rstudio offers Ubuntu as well as Debian versions
that can be installed with wget:

>>>>

            pdftitle={Git and Github Example and Tutorial, Sync with Multiple Repositories, Store Password},

@@

\title{Git and Github Example and Tutorial, Sync with Multiple Repositories,
Store Password}
\author{}
\date{\vspace{-2.5em}}

@@

\hypertarget{download-programs}{%
\section{Download Programs}\label{download-programs}}

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  Install \href{https://git-scm.com/download/win}{git for windows}:
  after install, try ``cd \textasciitilde{}/PyFan''
\item
  Install \href{https://atom.io/}{atom}
\item
  Might need to install \href{https://www.putty.org/}{putty} possibly
\end{enumerate}

\hypertarget{git-and-github-security-set-up}{%
\section{git and Github Security
Set-up}\label{git-and-github-security-set-up}}

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  open up git bash
\item
  generate rsa

  \begin{itemize}
  \tightlist
  \item
    \emph{ssh-keygen -t rsa -C
    ``\href{mailto:wangfanbsg75@live.com}{\nolinkurl{wangfanbsg75@live.com}}''}
  \item
    when prompted, do not enter ``file in which save the key'', when
    prompted for passphrase, enter ``WHATEVERPASSWORDIS''
  \end{itemize}
\item
  copy key

  \begin{itemize}
  \tightlist
  \item
    WINDOWS: \emph{clip \textless{} \textasciitilde{}/.ssh/id\_rsa.pub}
  \item
    LINUX: \emph{cat \textasciitilde{}/.ssh/id\_rsa.pub}
  \end{itemize}
\item
  log on to github ssh section, generate new ssh rsa key

  \begin{itemize}
  \tightlist
  \item
    SSH and GPG keys, choose New SSH key, paste in clipped text.
  \end{itemize}
\end{enumerate}

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{# inside git bash}
\FunctionTok{ssh-keygen}\NormalTok{ -t rsa -C }\StringTok{"wangfanbsg75@live.com"}
\CommentTok{# this copies the text in the .pub file generated}
\ExtensionTok{clip} \OperatorTok{<}\NormalTok{ ~/.ssh/id_rsa.pub}
\end{Highlighting}
\end{Shaded}

\hypertarget{start-and-sync-key-repositories}{%
\section{Start and Sync Key
Repositories}\label{start-and-sync-key-repositories}}

Inside git bash (open as \emph{administrator}), Sync Several Key
Repositories that should be synced on all computers:

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  fanwangecon.github.io: Github root repo
\item
  PyFan: Private Repo with Python Support Files
\item
  \href{https://github.com/FanWangEcon/Tex4Econ}{Tex4Econ}: Latex,
  installation, and various other support files, public repo.
\item
  \href{https://github.com/FanWangEcon/R4Econ}{R4Econ}: Public repo, R
  package, R research programs
\item
  \href{https://github.com/FanWangEcon/M4Econ}{M4Econ}: Public repo,
  Matlab package, Matlab examples and research files
\item
  \href{https://github.com/FanWangEcon/Py4Econ}{Py4Econ}: Public repo,
  Python package, Python research programs
\item
  Teaching: Private teaching repository
\end{enumerate}

Other repositories can be synced when needed on an ad-hoc basis. The
repositories above are essential repositories.

\hypertarget{repo-folders-and-global-config}{%
\subsection{Repo Folders and Global
config}\label{repo-folders-and-global-config}}

Remember git bash or bash should be in windows opened as
\emph{administrator}.

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{# cd to root folder}
\BuiltInTok{cd}\NormalTok{ ~}
\CommentTok{# generate all needed key repositories}
\FunctionTok{mkdir}\NormalTok{ fanwangecon.github.io PyFan Tex4Econ R4Econ M4Econ Py4Econ Teaching}

\CommentTok{# Set global config settings, in ~/.gitconfig}
\FunctionTok{git}\NormalTok{ config --global user.name }\StringTok{"Fan Wang"}
\FunctionTok{git}\NormalTok{ config --global user.email wangfanbsg75@live.com}
\end{Highlighting}
\end{Shaded}

\hypertarget{initalize-and-add-remote-repo-for-each}{%
\subsection{Initalize and add remote repo for
each:}\label{initalize-and-add-remote-repo-for-each}}

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{# Initialize Repositories}
\BuiltInTok{cd}\NormalTok{ ~/fanwangecon.github.io}
\FunctionTok{git}\NormalTok{ init}
\FunctionTok{git}\NormalTok{ remote add github git@github.com:fanwangecon/fanwangecon.github.io.git}
\BuiltInTok{cd}\NormalTok{ ~/PyFan}
\FunctionTok{git}\NormalTok{ init}
\FunctionTok{git}\NormalTok{ remote add github git@github.com:fanwangecon/PyFan}
\BuiltInTok{cd}\NormalTok{ ~/Tex4Econ}
\FunctionTok{git}\NormalTok{ init}
\FunctionTok{git}\NormalTok{ remote add github git@github.com:fanwangecon/Tex4Econ}
\BuiltInTok{cd}\NormalTok{ ~/R4Econ}
\FunctionTok{git}\NormalTok{ init}
\FunctionTok{git}\NormalTok{ remote add github git@github.com:fanwangecon/R4Econ}
\BuiltInTok{cd}\NormalTok{ ~/M4Econ}
\FunctionTok{git}\NormalTok{ init}
\FunctionTok{git}\NormalTok{ remote add github git@github.com:fanwangecon/M4Econ}
\BuiltInTok{cd}\NormalTok{ ~/Py4Econ}
\FunctionTok{git}\NormalTok{ init}
\FunctionTok{git}\NormalTok{ remote add github git@github.com:fanwangecon/Py4Econ}
\BuiltInTok{cd}\NormalTok{ ~/Teaching}
\FunctionTok{git}\NormalTok{ init}
\FunctionTok{git}\NormalTok{ remote add github git@github.com:fanwangecon/Teaching}
\end{Highlighting}
\end{Shaded}

\hypertarget{sync-repo-in-ssh-secure-session}{%
\subsection{Sync Repo in SSH Secure
Session}\label{sync-repo-in-ssh-secure-session}}

Pull latested from multiple repositories. Just Paste the following
lines.

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  start ssh-agent secure session
\item
  pull from multiple Repositories upon start of working session.
\item
  commit changes as work on one computer
\item
  upon leaving a computer with commited changes, push all
\item
  create bash file to make it easier to repeat steps
\end{enumerate}

Start and end ssh session:

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{# To avoid having to enter password each time, start background authentication agent.}
\BuiltInTok{eval} \StringTok{"}\VariableTok{$(}\FunctionTok{ssh-agent}\VariableTok{)}\StringTok{"}
\FunctionTok{ssh-add}\NormalTok{ ~/.ssh/id_rsa}

\CommentTok{# to stop the ssh session}
\BuiltInTok{kill} \VariableTok{$SSH_AGENT_PID}
\end{Highlighting}
\end{Shaded}

Pull from repos:

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{# Pull from Repositories, do these one by one first}
\BuiltInTok{cd}\NormalTok{ ~/fanwangecon.github.io}
\FunctionTok{git}\NormalTok{ pull github master}
\BuiltInTok{cd}\NormalTok{ ~/PyFan}
\FunctionTok{git}\NormalTok{ pull github master}
\BuiltInTok{cd}\NormalTok{ ~/Tex4Econ}
\FunctionTok{git}\NormalTok{ pull github master}
\BuiltInTok{cd}\NormalTok{ ~/R4Econ}
\FunctionTok{git}\NormalTok{ pull github master}
\BuiltInTok{cd}\NormalTok{ ~/M4Econ}
\FunctionTok{git}\NormalTok{ pull github master}
\BuiltInTok{cd}\NormalTok{ ~/Py4Econ}
\FunctionTok{git}\NormalTok{ pull github master}
\BuiltInTok{cd}\NormalTok{ ~/Teaching}
\FunctionTok{git}\NormalTok{ pull github master}
\end{Highlighting}
\end{Shaded}

Push from repos committed changes

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{# Push to Repositories, do these one by one first}
\BuiltInTok{cd}\NormalTok{ ~/fanwangecon.github.io}
\FunctionTok{git}\NormalTok{ push -u github master}
\BuiltInTok{cd}\NormalTok{ ~/PyFan}
\FunctionTok{git}\NormalTok{ push -u github master}
\BuiltInTok{cd}\NormalTok{ ~/Tex4Econ}
\FunctionTok{git}\NormalTok{ push -u github master}
\BuiltInTok{cd}\NormalTok{ ~/R4Econ}
\FunctionTok{git}\NormalTok{ push -u github master}
\BuiltInTok{cd}\NormalTok{ ~/M4Econ}
\FunctionTok{git}\NormalTok{ push -u github master}
\BuiltInTok{cd}\NormalTok{ ~/Py4Econ}
\FunctionTok{git}\NormalTok{ push -u github master}
\BuiltInTok{cd}\NormalTok{ ~/Teaching}
\FunctionTok{git}\NormalTok{ push -u github master}
\end{Highlighting}
\end{Shaded}

to create bash file to store these (from git bash in windows):

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{# store bash file in ~\textbackslash{}PyFan\textbackslash{}bin}
\FunctionTok{mkdir}\NormalTok{ ~/PyFan/bin}
\BuiltInTok{cd}\NormalTok{ ~/PyFan/bin}

\CommentTok{# create bash file}
\ExtensionTok{vim}\NormalTok{ pull_repos}
\ExtensionTok{vim}\NormalTok{ push_repos}

\CommentTok{# paste the text below over, comfirm bash loc with: which bash}
\CommentTok{#!/usr/bin/bash}
\BuiltInTok{echo}\NormalTok{ start fan github pull}
\CommentTok{# Security}
\BuiltInTok{eval} \StringTok{"}\VariableTok{$(}\FunctionTok{ssh-agent}\VariableTok{)}\StringTok{"}
\FunctionTok{ssh-add}\NormalTok{ ~/.ssh/id_rsa}
\CommentTok{# Pull from Persistent Repos}
\BuiltInTok{cd}\NormalTok{ ~/fanwangecon.github.io}
\FunctionTok{git}\NormalTok{ pull github master}
\CommentTok{# Stop Secured SSH}
\BuiltInTok{kill} \VariableTok{$SSH_AGENT_PID}

\CommentTok{# change permission to make file an executable}
\FunctionTok{chmod}\NormalTok{ u+x ~/PyFan/bin/pull_repos}
\FunctionTok{chmod}\NormalTok{ u+x ~/PyFan/bin/push_repos}
\CommentTok{# execute script}
\FunctionTok{bash}\NormalTok{ ~/PyFan/bin/pull_repos}
\end{Highlighting}
\end{Shaded}
